### 2023-12-07 thesis/sections/5.3-reference-resolution.tex
experiments

To do this, the model combines a representation of the image and a representation of the target object.
More specifically, the image is encoded using the \emph{image encoder} submodule

>>>>

To do this, the model combines a representation of the image and a representation of the target object.
More specifically, the image is encoded using the \emph{image encoder} submodule, omitting the last \emph{max pool} layer.
By this, the resulting matrix has 128\times14\times14 dimension, corresponding to the 14\time14 regions.
For the target object, the incremental RE is passed through an LSTM as described before.
Both encodings are passed through two linear layers separately to project them to the projection dimension $p$, followed by the $tanh$ function.
